---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# boxquickplot

<!-- badges: start -->
<!-- badges: end -->

The goal of boxquickplot is to provide users with a function to generate a boxplot figure in a single line. The figure has the added features of being organized in either ascending or descending order of the median of the plotted numerical variable for any desired number of categories to be included.

## Installation

You can install the development version of boxquickplot from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("stat545ubc-2021/functions-YFL-UBC/boxquickplot/")
```

## Example

This is a basic example which shows you a plot of a cancer dataset, obtained from [cBioPortal](https://www.cbioportal.org), to show the 15 deadliest cancer types by overall survival.

```{r example}
library(boxquickplot)
library(readr)
## basic example code
msk <- read_tsv("https://raw.githubusercontent.com/stat545ubc-2021/mini-data-analysis-EL/main/data/msk_impact_2017_clinical_data.tsv")
boxplot_10(msk, `Cancer Type`, `Overall Survival (Months)`, plot = 15, min_sample_size = 5, na.rm = T, .desc = F)
```
