---
title: "Assignment B-1"
output: md_document
---

```{r setup, message = FALSE}
library(tidyverse)
library(datateachr)
library(testthat)

```

# Function
We create a function that is able to plot a numerical variable across a categorical variable. It has the added feature of ensuring a readable plot will be obtained by filtering for 10 categories by median in either ascending or descending order. 

```{r f1}
#' boxplots for a dataframe
#'
#' This is a function to generate boxplots of a numerical variable across
#' a categorical variable, subsetting the data for 10 levels by either ascending
#' or descending order of the median. This ensures a visually interpretable
#' plot, where the categorical variable is plotted in the specified order.
#'
#' @param df dataframe to be plotted.
#'
#' @param categorical variable to be plotted on the x-axis.
#'
#' @param numerical variable to be plotted on the y-axis.
#'
#' @param min_sample_size a numerical scalar. Minimum group size to include
#' for plotting. Low sample size may produce highly skewed boxplots.
#'
#' @param na.rm a logical scalar. Whether NA's should be excluded in the
#' calculation of medians.
#'
#' @param .desc specifies whether groupings are selected based on ascending
#' or descending medians. Follows the notation of the forcats package.
#'
#' @return output will be a plot provided a dataset and the corresponding
#' categorical and numerical vaiables are specified. Otherwise, will return a
#' warning.
boxplot_10 <- function(df, categorical, numerical, min_sample_size = 10, na.rm = TRUE, .desc = FALSE) {
  #check that a dataframe hsa been inputted
  if (is.vector(df)) {
    stop("df must be a dataframe. You inputted an object of the type: ", class(df))
  }
    
  # calculate medians and filter by minimum sample size
  top_10 <- df %>%
    group_by({{ categorical }}) %>%
    summarize(median = median({{ numerical }}, na.rm = na.rm), count = n()) %>%
    filter(count > min_sample_size)

  # order categorical in ascending or descending order
  if (.desc == T) {
    top_10 <- top_10 %>%
      arrange(desc(median)) %>%
      head(10) %>%
      pull({{ categorical }})
  } else {
    top_10 <- top_10 %>%
      arrange(median) %>%
      head(10) %>%
      pull({{ categorical }})
  }

  # filter for variables to be plotted and set levels
  df_10 <- df %>%
    filter({{ categorical }} %in% top_10 & !is.na({{ numerical }})) %>%
    mutate(categorical = fct_reorder({{ categorical }}, {{ numerical }}, na.rm = na.rm, .desc = .desc))
  # ggplot automatically removes NA but will return a warning
  
  # ggplot visualization
  ggplot(df_10, aes(
    x = categorical,
    y = {{ numerical }},
    color = categorical
  )) +
    geom_boxplot(outlier.color = "black", outlier.size = 0.5) +
    theme(
      axis.text.x = element_text(size = 6, angle = 45, vjust = 1, hjust = 1),
      legend.position = "none"
    ) +
    xlab(element_blank())
}
```

# Examples

**Example 1.** A clinical cancer dataset is used to plot overall survival for different cancer types. We choose a minimum sample size of 5, and order the types in descending order of median overall survival.
```{r e1}
#load and preview the dataset
msk <- read_tsv("https://raw.githubusercontent.com/stat545ubc-2021/mini-data-analysis-EL/main/data/msk_impact_2017_clinical_data.tsv")

head(msk)

boxplot_10(msk, `Cancer Type`, `Overall Survival (Months)`, min_sample_size = 5, na.rm = T, .desc = T)
```
**Example 2.** A dataset on vancouver trees from the datateachr package is used to create a plot of the tree genera with the greatest median altitude, as a indicator of which trees tend to be located more north.

```{r e2}
boxplot_10(vancouver_trees, genus_name, latitude, .desc = T, min_sample_size =  100)
```

**Example 3.** We use another dataset from datateachr, this time for steam games, to visualize the discount for games of different genres.

```{r e3}
boxplot_10(steam_games, genre, discount_price, min_sample_size =  20, .desc = T)
```
# Testing the function

```{r t1}
# check the output type of our function
test_that("Function outputs a boxplot", {
  p <- boxplot_10(msk, `Cancer Type`, `Overall Survival (Months)`, min_sample_size = 5, na.rm = T, .desc = T) 
  # class of the output should be a ggplot object
  expect_s3_class(p ,"ggplot") 
  # check that geom layer is a boxplot
  expect_identical(class(p$layers[[1]]$geom)[1], "GeomBoxplot")
})
```

```{r t2}
# create a test inputting arguments that cannot be plotted
test_that("Function requires correct argument input types", {
  # numeric scalar as only argument
  expect_error(boxplot_10(1))
   # logical scalar as only argument
  expect_error(boxplot_10(T))
  # list as only argument
  expect_error(boxplot_10(list(c(1,2,3), c("A","B","C"))))
})
```